
---
title: "Stat 538 - HW7"
author: "FirstName LastName"
output: word_document
---

# General

```{r}
library(car)
library(svglite)
```

setwd("~/Repos/Stat538_homeworks/7")

# S6.5

## S6.5.a

To make a judgement call on whether transformation is a good idea or not we should look at the residuals and QQ plots.

```{r s6.5.a}
# Load the dataset
pgatour <- read.csv("Data/pgatour2006.csv")

# Define the predictors
predictors <- c("DrivingAccuracy", "GIR", "PuttingAverage", 
                "BirdieConversion", "SandSaves", "Scrambling", "PuttsPerRound")
formula_untransformed <- as.formula(paste("PrizeMoney ~", paste(predictors, collapse = " + ")))
formula_log <- as.formula(paste("log(PrizeMoney) ~", paste(predictors, collapse = " + ")))

# Fit both models
fit_orig <- lm(formula_untransformed, data = pgatour)
fit_log  <- lm(formula_log, data = pgatour)

# Generate Diagnostic Plots
par(mfrow = c(2, 2))

# Model 1: Untransformed (Check for funnel shape in Resids vs Fitted and curve in Q-Q)
plot(fit_orig, which = 1, main = "Untransformed: Residuals vs Fitted")
plot(fit_orig, which = 2, main = "Untransformed: Normal Q-Q")

# Model 2: Log-transformed (Expect constant spread and straight Q-Q line)
plot(fit_log, which = 1, main = "Log-transformed: Residuals vs Fitted")
plot(fit_log, which = 2, main = "Log-transformed: Normal Q-Q")
```

As we can see from the above plots, the log-transformation actually helps with the assumptions of normality. Before the log tranformation the assumptions of normality were violated but the log-transformation helps with that.

## S6.5.b

```{r S6.5.b}
# Fit the full model
full_model <- lm(log(PrizeMoney) ~ DrivingAccuracy + GIR + PuttingAverage + 
                   BirdieConversion + SandSaves + Scrambling + PuttsPerRound, data=pgatour)

# Diagnostic Plots
par(mfrow=c(2,2))
plot(full_model)
```

Per the plots, it seems that the assumptions of the Gauss-Markov model are left largely intact *when* the predicted value is log-transformed before-hand. As such, the model should be fine to use.


## S6.5.c

Generally the points worth investigating are:

1. High Leverage Points
2. Outiers
3. Influential points

```{r S6.5.c}
library(ggplot2)
library(ggrepel)

# 1. Create a diagnostic dataframe
diag_data <- data.frame(
  Index = 1:nrow(pgatour),
  StudentizedResid = rstudent(full_model),
  HatValues = hatvalues(full_model),
  CooksD = cooks.distance(full_model)
)

# 2. thresholds for labeling
# High influence: Cook's D > 4/n
# High leverage: Hat > 2p/n (where p is 8 including intercept)
threshold_cook <- 4 / nrow(pgatour)
threshold_hat <- (2 * 8) / nrow(pgatour)

# 3. Visualization using ggplot2
ggplot(diag_data, aes(x = HatValues, y = StudentizedResid)) +
  geom_point(aes(size = CooksD, color = CooksD > threshold_cook), alpha = 0.7) +
  geom_hline(yintercept = c(-3, 0, 3), linetype = "dashed", color = "red") +
  geom_vline(xintercept = threshold_hat, linetype = "dotted") +
  scale_color_manual(values = c("black", "firebrick")) +
  geom_text_repel(data = subset(diag_data, CooksD > threshold_cook | abs(StudentizedResid) > 2.5),
                  aes(label = Index), size = 3) +
  labs(title = "Influence Plot: Studentized Residuals vs Leverage",
       subtitle = "Size of point proportional to Cook's Distance",
       x = "Leverage (Hat Values)",
       y = "Studentized Residuals") +
  theme_minimal() +
  guides(color = "none")
```

## S6.5.d

In linear regression, the usual suspect for model weakness is multi-collinearity. To calculate and account for that the first thing we can do is check for the Variance Inflation Factor. Which you can do as follows:

```{r}
library(car)
vif_values <- vif(full_model)
print(vif_values)

# Visualization of VIF
barplot(vif_values, main = "VIF Values", horiz = TRUE, col = "steelblue", las = 1)
abline(v=5, lwd=3, lty=2, col="red")
```
It seems `GIR`, `PuttsPerRound` and `PuttingAverage` have exceptionally high VIFs (>5). Not accounting for these means that the final variance/error is severely inflated.


We can also use a correlation matrix to visualize this.
```{r}
library(corrplot)
corr_matrix <- cor(pgatour[, c("DrivingAccuracy", "GIR", "PuttingAverage", 
                           "BirdieConversion", "SandSaves", "Scrambling", "PuttsPerRound")])
corrplot(corr_matrix, method = "color", addCoef.col = "black", number.cex = 0.7)
```

As we can see, the correlation matrix shows a strong positive correlation (0.79) between these two variables (`PuttsPerRound` and `PuttingAverage` and a strong negative correlation (-0.77) between `PuttingAverage` and `BirdieConversion`.

## S6.5.e

It is generally a bad idea to remove points from a model for any reason other than feasibility (i.e. your data is incomputable because of size), let alone convenance. You could make the model unstable by removing various variables at once. The underlying data maybe too small to be useful or not capture a real spread of the underlying experiment. If the predictors are correlated then then it isn't always clear what the impact of something is. If the impact of one predictor is confounded by co-linearity with another then what seems insignificant in correlation is significant by itself.